Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2019-12-06 manuscript/climate_sensitivity_draft.Rmd
Update climate_sensitivity_draft.Rmd
title & keywords

**Title:** Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf deciduous forest **see comment KAT**

@@

**coauthors, fill in middle initials and affiliations, if missing***

@@

*Key words*:  canopy position; drought; Forest Global Earth Observatory (ForestGEO); leaf hydraulic traits; temperate broadleaf deciduous forest; tree growth; tree height; tree-ring [5-8] *Five to eight key words (in alphabetical order) . Words that are in the title can, and should, be among these.* **See comment 3 **

>>>>

**Title:** Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

@@

@@

*Key words*:  canopy position; drought; Forest Global Earth Observatory (ForestGEO); leaf hydraulic traits; temperate broadleaf deciduous forest; annual growth; tree height; tree-ring [5-8] *Five to eight key words (in alphabetical order) . Words that are in the title can, and should, be among these.*
